EDA

### 2020-02-27 src/draft.Rmd
added multiplot and aes

@@

@@

4. box plots of mill rates, grouped by region
```{r}
rate_boxes <- ggplot(dat_rate, aes(x=AddressAssessorMunicipalityDesc,y=rate,fill=TaxClassCode)) + geom_boxplot() + facet_wrap(~TaxClassCode)
rate_boxes
```

>>>>

multiplot(rate_class1, rate_class5, rate_class6)

@@

multiplot(assess_class1, assess_class5, assess_class6)

@@

4. box plots of mill rates, grouped by region
```{r}
rate_boxes <- ggplot(dat_rate, aes(x=AddressAssessorMunicipalityDesc,y=rate,fill=TaxClassCode)) + geom_boxplot() + facet_wrap(~TaxClassCode)
rate_boxes + theme(axis.text.x = element_text(angle = 90, hjust = 1))
```
